Asimilación de distintas observaciones

### 2020-12-04 analysis/chapters/experimento_20181122.Rmd
Mejoro fig de corte zonal

```{r}
q[date == unique(date)[1:3] & west_east %between% c(70, 180)] %>% 
  .[, .(q_mean = mean(q),
        v_mean = mean(v)), by = .(bottom_top, south_north, date, exp)] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(south_north, bottom_top)) +
  geom_contour_fill(aes(z = q_mean*1000, fill = stat(level_d))) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour(aes(z = v_mean, linetype = factor(-sign(..level..))), 
               color = "grey30", size = 0.5, binwidth = 2) +
  geom_text_contour(aes(z = v_mean), color = "grey30", stroke = 0.1, breaks = seq(-10, 6, 2)) +
  scale_linetype(guide = NULL) +
  # geom_vector(aes(x = south_north, y = bottom_top,
  #                 mag = abs(v_mean), angle = fifelse(v_mean > 0, 0, 180)),
  #             arrow.angle = 6, size = 0.2, skip.x = 10) +
  # scale_mag() +
  facet_grid(date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  labs(y =  "Sigma levels", x = "Grid points") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

>>>>

```{r}
q[date == unique(date)[1:3] & west_east %between% c(70, 180)] %>% 
  .[, .(q_mean = mean(q),
        v_mean = mean(v)), by = .(bottom_top, south_north, date, exp)] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(south_north, bottom_top)) +
  geom_contour_fill(aes(z = q_mean*1000, fill = stat(level_d))) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour(aes(z = v_mean, linetype = factor(-sign(..level..))), 
               color = "grey30", size = 0.3, binwidth = 2) +
  geom_text_contour(aes(z = v_mean), color = "grey30", size = 4, stroke = 0.1, breaks = seq(-10, 6, 2)) +
  scale_linetype(guide = NULL) +
  # geom_vector(aes(x = south_north, y = bottom_top,
  #                 mag = abs(v_mean), angle = fifelse(v_mean > 0, 0, 180)),
  #             arrow.angle = 6, size = 0.2, skip.x = 10) +
  # scale_mag() +
  facet_grid(date ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  labs(y =  "Sigma levels", x = "Grid points") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```
